On Secure Delegation of SampBQP with a Classical Client

### 2020-02-07 qpip0.tex

\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
\label{proto:QPIP0samp}
\begin{enumerate}
%    \item Verifier start with description of quantum circuit $C$, input string $x$ 
    \item Both verifier and prover start with the description of number of qubits $n$, quantum circuit $C$, input string $x$, and  a soundness parameter $\varepsilon$.
    \item Run $N=O(1/\varepsilon)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications. On the second round, for each copy, the prover choose the state specified by Protocol~\ref{ProtoQPIP1}  (with error $\eps$) as $\rho$. On the third round, the verifier uniformly randomly pick an $i\in [N]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies.
    \item \label{step:multi-testing}Verifier rejects if the results on any of the test rounds is rejected. 
    \item If all testing rounds are accepted, verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
\end{enumerate}
\end{protocol}

@@

By Lemma~\label{lem:partition}

@@

\begin{lemma}[Slight adaption from Lemma 3.5 of \cite{parallelrep}]\label{lem:partition}
Let $(U_0,U)$ be any prover's strategy in Protocol~\ref{proto:QPIP0samp}. Let $m=O(\log \secpar)$, $i\in[m]$, 
$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\frac{\gamma_0}{T}=1/\poly(\secpar)$. Let $\gamma$ be sampled uniformly randomly from $[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}]$. Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{\regX,\regZ}$,  
\begin{align*}
    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+ z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
\end{align*}
where $t$ is the number of qubits in the register $ph$, $z_0,z_1\in \mathbb{C}$ such that $|z_0|=|z_1|=1$, and 
$z_0$, $z_1$, $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ may depend on $\gamma$.

Furthermore, the following properties are satisfied.
%
\begin{enumerate}
%\item There exist (sub-normalized) states $\ket{\psi_0}_{\regX,\regZ}$ and $\ket{\psi_1}_{\regX,\regZ}$ such that when $G_{i,\gamma}$ runs on input $\ket{\psi}_{\regX,\regZ}$, the output is  $(0,\ket{\psi_0}_{\regX,\regZ}/\|\ket{\psi_0}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_0}_{\regX,\regZ}\|^2$, $(1,\ket{\psi_1}_{\regX,\regZ}/\|\ket{\psi_1}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_1}_{\regX,\regZ}\|^2$, and $\bot$ with probability  $1-\|\ket{\psi_0}_{\regX,\regZ}\|^2- \|\ket{\psi_1}_{\regX,\regZ}\|^2$,
    \item If we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$, then we have  $E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$.
\item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$. %where $M_{ph,th,in}$ is the computational-basis measurement in the register $(ph,th,in)$. %and $t$ is the number of qubits in $ph$.   
This implies that if we apply the measurement $M_{ph,th,in}$ on $\frac{G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in}}{\|\ket{\psi}_{\regX,\regZ}\|}$, then the outcome is $0^tb1$ with probability $\|\ket{\psi_b}_{\regX,\regZ}\|^2$ and the resulting state in the register $(\regX,\regZ)$  is $\frac{\ket{\psi_b}_{\regX,\regZ}}{\|\ket{\psi_b}_{\regX,\regZ}\|}$ ignoring a global phase factor.
    \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. 
        \item 
For any fixed $\gamma$ and $c\in \bit^m$ such that $c_i=0$, we have 
\begin{align*}
\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq 2^{m-1}\gamma+\negl(\secpar).
\end{align*}
    \item 
For any fixed $\gamma$, there exists an efficient quantum algorithm $\ext_i$ such that 
\begin{align*}  
  \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
  \end{align*}   
\end{enumerate}
\end{lemma}

>>>>

\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
\label{proto:QPIP0samp}
\begin{enumerate}
%    \item Verifier start with description of quantum circuit $C$, input string $x$ 
    \item Both verifier and prover start with the description of number of qubits $n$, quantum circuit $C$, input string $x$, and  a soundness parameter $\varepsilon$.
    \item Run $m=O(1/\varepsilon)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications. On the second round, for each copy, the prover choose the state specified by Protocol~\ref{ProtoQPIP1}  (with error $\eps$) as $\rho$. On the third round, the verifier uniformly randomly pick an $i\in [m]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies.
    \item \label{step:multi-testing}Verifier rejects if the results on any of the test rounds is rejected. 
    \item If all testing rounds are accepted, verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
\end{enumerate}
\end{protocol}

@@

Choose the $T$ in Lemma~\ref{lem:partition} to be $\Theta(m^3)$ \hannote{$\gamma_0$?}. By Property~\ref{partition-property-1} of Lemma~\ref{lem:partition}, 
$$\forall i, \L(1- 1/m^2\R)\text{fraction of }\gamma$$ 
satisfies that 
$$\norm{\ket{\psi_{err}}}^2 \leq 1/m+\negl(n). $$
Therefore, there exist an $\gamma$ such that 
$$\forall i,\, \norm{\ket{\psi_{err}}}^2 \leq 1/m+\negl(n). $$

Denote $G_{i,\gamma}$ with  $\gamma$ found above as $G_i$.

@@

\begin{lemma}[Slight adaption from Lemma 3.5 of \cite{parallelrep}]\label{lem:partition}
Let $(U_0,U)$ be any prover's strategy in Protocol~\ref{proto:QPIP0samp}.  $i\in[m]$, 
$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\frac{\gamma_0}{T}=1/\poly(\secpar)$. Let $\gamma$ be sampled uniformly randomly from $[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}]$. Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{\regX,\regZ}$,  
\begin{align*}
    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+ z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
\end{align*}
where $t$ is the number of qubits in the register $ph$, $z_0,z_1\in \mathbb{C}$ such that $|z_0|=|z_1|=1$, and 
$z_0$, $z_1$, $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ may depend on $\gamma$.

Furthermore, the following properties are satisfied.
%
\begin{enumerate}
%\item There exist (sub-normalized) states $\ket{\psi_0}_{\regX,\regZ}$ and $\ket{\psi_1}_{\regX,\regZ}$ such that when $G_{i,\gamma}$ runs on input $\ket{\psi}_{\regX,\regZ}$, the output is  $(0,\ket{\psi_0}_{\regX,\regZ}/\|\ket{\psi_0}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_0}_{\regX,\regZ}\|^2$, $(1,\ket{\psi_1}_{\regX,\regZ}/\|\ket{\psi_1}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_1}_{\regX,\regZ}\|^2$, and $\bot$ with probability  $1-\|\ket{\psi_0}_{\regX,\regZ}\|^2- \|\ket{\psi_1}_{\regX,\regZ}\|^2$,
    \item \label{partition-property-1} If we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$, then we have  $E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$. 
\item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$. %where $M_{ph,th,in}$ is the computational-basis measurement in the register $(ph,th,in)$. %and $t$ is the number of qubits in $ph$.   
This implies that if we apply the measurement $M_{ph,th,in}$ on $\frac{G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in}}{\|\ket{\psi}_{\regX,\regZ}\|}$, then the outcome is $0^tb1$ with probability $\|\ket{\psi_b}_{\regX,\regZ}\|^2$ and the resulting state in the register $(\regX,\regZ)$  is $\frac{\ket{\psi_b}_{\regX,\regZ}}{\|\ket{\psi_b}_{\regX,\regZ}\|}$ ignoring a global phase factor.
    \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. 
        \item 
For any fixed $\gamma$ and $c\in \bit^m$ such that $c_i=0$, we have 
\begin{align*}
\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq 2^{m-1}\gamma+\negl(\secpar).
\end{align*}
    \item 
For any fixed $\gamma$, there exists an efficient quantum algorithm $\ext_i$ such that 
\begin{align*}  
  \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
  \end{align*}   
\end{enumerate}
\end{lemma}
